Testing Quasar Unification: I. Radiative Transfer in Clumpy Winds

### 2016-02-08 paper.tex
removed atomic data sentence

\subsection{Atomic Data}
We use the same atomic data  described by LK02 as updated by H13 and M15.
As in M15, macro-atom level information comes from \textsc{Topbase} \citep{cunto1993}.
H and He~\textsc{ii} are treated with 10 levels, and we include one He~\textsc{i} 
level. This is because He is almost always completely ionized 
and so He~\textsc{i} is unimportant in the simulation.
% with the addition of direct (collisional) ionization and recombination
% data from \cite{dere2007}. 
Photoionization cross-sections are from \textsc{Topbase} \citep{cunto1993} and \cite{vfky}.
Dielectronic and Radiative recombination rate coefficients for simple-atoms are taken from 
the \textsc{Chianti} database version 7.0 \citep{dere1997,landi2012}.
We use ground state recombination rates from \cite{badnell2006} where available,
and otherwise default to calculating recombination rates from the Milne
relation. Free-free Gaunt factors are from \cite{sutherland1998}.

>>>>

\subsection{Atomic Data}
We use the same atomic data  described by LK02 as updated by H13 and M15.
As in M15, macro-atom level information is from \textsc{Topbase} \citep{cunto1993}.
Photoionization cross-sections are from \textsc{Topbase} \citep{cunto1993} and \cite{vfky}.
Dielectronic and Radiative recombination rate coefficients for simple-atoms are taken from 
the \textsc{Chianti} database version 7.0 \citep{dere1997,landi2012}.
We use ground state recombination rates from \cite{badnell2006} where available,
and otherwise default to calculating recombination rates from the Milne
relation. Free-free Gaunt factors are from \cite{sutherland1998}.
